Ranking of Classification Algorithms in AutoML

### 2017-12-06 Writing/Proposal/Tex/paper.tex
Cleanup of proposal presentation and tex files.
Further minor corrections in proposal + title change.

\usepackage{graphicx}
\graphicspath{{images/}}

@@

\title{Automatic Ranking of Classification Algorithms}
\subtitle{A Comparison of Regression-Based Ranking and Preference Models
\\\vspace{2em}Bachelor's Thesis Proposal \& Work Plan}

@@

\section{Related Work}\label{sec:related_work}
The demand for aid in the process of selecting an algorithm has already led to the development of tools that automate machine-learning (AutoML). In the following paragraphs, three of those tools work are outlined briefly.\\

@@

% SK-learn
AUTO-SKLEARN has been described as a sister-package to Auto-WEKA and is an AutoML tool which is based on scikit-learn, a machine learning library for Python \cite{feurer2015efficient}. It works very similar to AutoML but extends it by adding a meta-learning pre-processing step to warmstart the Bayesian Optimization and automatically constructing ensembles during optimization. During the pre-processing phase, performance values for the classifiers available in AUTO-SKLEARN are recorded on a set of data sets. For each data set, the algorithm which shows the best empirical performance is noted. Then, certain meta-features are calculated for each data set. The first step of the tool when given a new problem is to calculate meta-features of the data set. Then, the Manhattan distance to the other data sets is determined according to the meta-features, and the algorithms that are associated with the k-nearest data sets are used as a starting point for further optimization. The authors observe that the additional meta-learning and ensemble construction result in a more efficient and robust application. Their results show that Meta-Learning can be used to improve the overall AutoML process.\\

@@

\section{Goals}\label{sec:goals}
The aim of this thesis is to test the assumption that given a new data set, one can derive an accuracy-based ranking of classification algorithms from their past performances by means of regression-based compared with preference-based ranking, and to compare the two methods. It is derived from the need for AutoML tools and the fact that related solutions so far have not exploited Meta-Learning in this way. If the hypothesis is true, this tool could be used as a pre-processing step in another Auto-ML framework similarly to how Meta-Learning is used in AUTO-SKLEARN, as a pre-processing step to speed up the whole process. The aim presented consists of multiple goals, which can be divided into required and optional goals.

@@

The first step therefore is to implement the pre-processing phase, which consist of computing the performances of classifiers on data sets. For the implementation of the classifiers, WEKA 3.8.1 is going to be used, which dictates the set of classifiers that will be included\footnotemark. The data sets will be fetched from OpenML.org, an open-source project where users can contribute data sets, implementations for machine learning algorithms, and run algorithm runs. Since the results of the runs are available publicly on the website, some of the required data may be extracted instead of computed. OpenML.org provides the data sets in .ARFF format, and supplies a WEKA plug-in, which should ensure that these libraries work together smoothly. \\

\footnotetext{Meta-Classifiers and Ensemble-Classifiers will not be supported.}

@@

For the evaluation, it is necessary to generate a baseline and an oracle. Both can be obtained from the data of the pre-processing phase. Due to all performances of classifiers being recorded on all data sets, one can obtain an optimal ranking of classifiers for each data set from that same table. The baseline which is going to be used is counting the number of data sets for which a classifier is the best option, and then ranking them from overall best performance (best choice for most data sets) to worst. This can be obtained from the table of the pre-processing phase as well. The rankings of the oracle, the baseline, and the results of the tool are then going to be compared using the Kendall Rank Correlation Coefficient.

@@

\newpage
\section{Schedule}\label{sec:schedule}
The working time is going to be structured according to the schedule shown in figure \ref{fig:schedule}. Variations due to unforeseeable circumstances may occur.

>>>>

\usepackage{graphicx}

@@

\title{Ranking of Classification Algorithms in AutoML}
\subtitle{A Comparison of Regression-Based Ranking and Preference Models
\\\vspace{2em}Bachelor's Thesis Proposal \& Work Plan}

@@

\section{Related Work}\label{sec:related_work}
The demand for aid in the process of selecting an algorithm has already led to the development of tools that automate machine-learning (AutoML). In the following paragraphs, three of such tools are outlined briefly.\\

@@

% SK-learn
AUTO-SKLEARN has been described as a sister-package to Auto-WEKA and is an AutoML tool which is based on scikit-learn, a machine learning library for Python \cite{feurer2015efficient}. It works very similar to AutoML but extends it by adding a meta-learning pre-processing step to warmstart the Bayesian optimization and automatically constructing ensembles during optimization. During the pre-processing phase, performance values for the classifiers available in AUTO-SKLEARN are recorded on a set of data sets. For each data set, the algorithm which shows the best empirical performance is noted. Then, certain meta-features are calculated for each data set. The first step of the tool when given a new problem is to calculate meta-features of the data set. Then, the Manhattan distance to the other data sets is determined according to the meta-features, and the algorithms that are associated with the k-nearest data sets are used as a starting point for further optimization. The authors observe that the additional meta-learning and ensemble construction result in a more efficient and robust application. Their results show that meta-learning can be used to improve the overall AutoML process.\\

@@

\section{Goals}\label{sec:goals}
The aim of this thesis is to test the assumption that given a new data set, one can derive an accuracy-based ranking of classification algorithms from their past performances by means of regression-based compared with preference-based ranking, and to compare the two methods. It is derived from the need for AutoML tools and the fact that related solutions so far have not exploited meta-learning in this way. If the hypothesis is true, this tool could be used as a pre-processing step in another Auto-ML framework similarly to how meta-learning is used in AUTO-SKLEARN, as a pre-processing step to speed up the whole process. The aim presented consists of multiple goals, which can be divided into required and optional goals.

@@

The first step therefore is to implement the pre-processing phase, which consist of computing the performances of classifiers on data sets. For the implementation of the classifiers, WEKA 3.8.1 is going to be used, which dictates the set of classifiers that will be included\footnotemark. The data sets will be fetched from OpenML.org, an open-source project where users can contribute data sets, implementations for machine learning algorithms, and algorithm runs. Since the results of the runs are available publicly on the website, some of the required data may be extracted instead of computed. OpenML.org provides the data sets in .ARFF format, and supplies a WEKA plug-in, which should ensure that these libraries work together smoothly. \\

\footnotetext{Meta-classifiers and ensemble-classifiers will not be supported.}

@@

For the evaluation, it is necessary to generate a baseline and an oracle. Both can be obtained from the data of the pre-processing phase. Due to all performances of classifiers being recorded on all data sets, one can obtain an optimal ranking of classifiers for each data set from that same table. The baseline which is going to be used is counting the number of data sets for which a classifier is the best option, and then ranking them from overall best performance (best choice for most data sets) to worst. This can be obtained from the table of the pre-processing phase as well. The rankings of the oracle, the baseline, and the results of the tool are then going to be compared using the Kendall rank correlation coefficient.

@@

\newpage
\section{Schedule}\label{sec:schedule}
The working time is going to be structured according to the schedule shown in Figure \ref{fig:schedule}. Variations due to unforeseeable circumstances may occur.
